Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-13 journal paper/journal_main.tex
updates to intro + numerical sections
Inserted some \newpage commands.
Removed page number from ToC.
Added \newpage in the appendix.
Removed "first version" from \date.
Inserted a \newpage.
Moved "background" to Appendix A.
Revised some appendix titles.
Changed ToC to small font.
correcting ack

\author{Guy Aridor%
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu}
\and
%\rule{0.2in}{0pt}
Yishay Mansour%
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com}
\and
%\rule{0.2in}{0pt}
Aleksandrs Slivkins%
\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com}
\and
%\rule{0.2in}{0pt}
Zhiwei Steven Wu%
\footnote{University of Minnesota - Twin Cities, Department of Computer Science. Email: zsw@umn.edu\newline
The research has been done when Z.S. Wu has been an intern and a postdoc at Microsoft Research NYC.
}}
\date{First version: July 2020}
\maketitle
\begin{abstract}
Most online platforms strive to learn from interactions with consumers, and many engage in \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information. We initiate a study of the interplay between \emph{exploration} and \emph{competition}: how such platforms balance the exploration for learning and the competition for consumers. Here consumers play three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents which choose among the competing platforms.

@@

\bigskip
\end{abstract}
%\setcounter{page}{0}
%\thispagestyle{empty}
%\end{titlepage}

\newpage
\begin{small}
\setcounter{tocdepth}{2}
\tableofcontents
\end{small}
\newpage

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\section{Introduction}
\label{sec:intro}
\subfile{content/sec-intro}

@@

\section{Theoretical results: the \TheoryModel}
\label{sec:theory}
\subfile{content/sec-theory}

@@

\gaedit{
\subfile{content/conclusion}
}

\clearpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{plainnat}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}

@@

\section{Background on multi-armed bandits}
\label{app:examples}
\subfile{itcs18paper/app-examples}

@@

\section{Proofs for Section~\ref{sec:theory}}
\label{sec:theory-proofs}
\subfile{content/sec-theory-proofs}

>>>>

\author{Guy Aridor%
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu}
\and
%\rule{0.2in}{0pt}
Yishay Mansour%
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com}
\and
%\rule{0.2in}{0pt}
Aleksandrs Slivkins%
\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com}
\and
%\rule{0.2in}{0pt}
Zhiwei Steven Wu%
\footnote{University of Minnesota - Twin Cities, Department of Computer Science. Email: zsw@umn.edu\newline
Part of the research was done when Z.S. Wu was an intern and a postdoc at Microsoft Research NYC.
}}
\date{July 2020}
\maketitle
\begin{abstract}
Most online platforms strive to learn from interactions with consumers, and many engage in \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information. We initiate a study of the interplay between \emph{exploration} and \emph{competition}: how such platforms balance the exploration for learning and the competition for consumers. Here consumers play three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents which choose among the competing platforms.

@@

\bigskip
\end{abstract}
\setcounter{page}{0}
\thispagestyle{empty}
%\end{titlepage}

\newpage
\begin{small}
\setcounter{tocdepth}{2}
\tableofcontents
\end{small}
\setcounter{page}{0}
\thispagestyle{empty}
\newpage

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\section{Introduction}
\label{sec:intro}

\subfile{content/sec-intro}

@@

\newpage
\section{Theoretical results: the \TheoryModel}
\label{sec:theory}
\subfile{content/sec-theory}

@@

\newpage
\gaedit{
\subfile{content/conclusion}
}

\newpage
\addcontentsline{toc}{section}{References}

\bibliographystyle{plainnat}
\begin{small}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}
\end{small}

@@

\section{Background for non-specialists: the three classes of algorithms [IN PROGRESS]}
\label{sec:related-classes}
\subfile{content/sec-bg}

\section{Auxiliary theoretical results}
\label{app:examples}
\subfile{itcs18paper/app-examples}

@@

\newpage
\section{Full proofs for Section~\ref{sec:theory}}
\label{sec:theory-proofs}
\subfile{content/sec-theory-proofs}

\newpage
\section{Full experimental results}
\label{app:expts}
